### 2021-12-02 plos_latex_template.tex
RJ: added author contributions (for now)

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules towards hosting an inclusive conference} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rocío Joo\textsuperscript{1*}, %,2\Yinyang},
Andrea Sánchez-Tapia\textsuperscript{2},
Sara Mortara\textsuperscript{3},
Heather Turner\textsuperscript{4}, %\ddag},
Dorothea Hug Peter\textsuperscript{5}, %\ddag},
Matt Bannert\textsuperscript{6},
Batool Almazrouq\textsuperscript{7},
Liz Hare\textsuperscript{8},
Janani Ravi\textsuperscript{9},
Laura Ación\textsuperscript{10},
Juan Pablo Narváez\textsuperscript{11},
Marcela Alfaro Córdoba\textsuperscript{12},
Federico Marini\textsuperscript{13},
Rita Giordano\textsuperscript{14},
Natalia Morandeira\textsuperscript{15},
Adithi Upadhya\textsuperscript{16},
Joselyn Chávez\textsuperscript{17\Yinyang},
Anicet Ebou\textsuperscript{18\Yinyang},
Silvia Canelón\textsuperscript{19\Yinyang},
Yanina Bellini Saibene\textsuperscript{20}%,3\textcurrency}
\\
\bigskip
\textbf{1} Global Fishing Watch, Washington, DC 20036, USA
\\
\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{4} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{5} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{6} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{7} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{8} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{9} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{10} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{11} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{12} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{13} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{14} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{15} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{16} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{17} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{18} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{19} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{20} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules towards hosting an inclusive conference} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rocío Joo\textsuperscript{1*}, %,2\Yinyang},
Andrea Sánchez-Tapia\textsuperscript{2},
Sara Mortara\textsuperscript{3},
Yanina Bellini Saibene\textsuperscript{4},
Heather Turner\textsuperscript{5}, %\ddag},
Dorothea Hug Peter\textsuperscript{6}, %\ddag},
Matt Bannert\textsuperscript{7},
Batool Almazrouq\textsuperscript{8},
Liz Hare\textsuperscript{9},
Laura Ación\textsuperscript{10},
Juan Pablo Narváez\textsuperscript{11},
Marcela Alfaro Córdoba\textsuperscript{12},
Federico Marini\textsuperscript{13},
Rita Giordano\textsuperscript{14},
Natalia Morandeira\textsuperscript{15},
Adithi Upadhya\textsuperscript{16},
Joselyn Chávez\textsuperscript{17\Yinyang},
Anicet Ebou\textsuperscript{18\Yinyang},
Silvia Canelón\textsuperscript{19\Yinyang},
Janani Ravi\textsuperscript{20}
%,3\textcurrency}
\\
\bigskip
\textbf{1} Global Fishing Watch, Washington, DC 20036, USA
\\
\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{4} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{5} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{6} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{7} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{8} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{9} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{10} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{11} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{12} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{13} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{14} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{15} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{16} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{17} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{18} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{19} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{20} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

\section*{Authors' contributions}

To list author contributions, we used the high-level contributor roles in the CRediT framework relevant for this study (project administration, supervision, writing original draft, conceptualization, writing—major reviews and edits, resources, and visualization; \url{http://credit.niso.org}), and an additional category for contributions on their own ten simple rules for an inclusive conference without looking at the first draft (i.e. sharing rules).

\begin{itemize}
    \item RJ: Project administration, Supervision, Writing original draft, Conceptualization, Writing--major reviews and edits, Resources, Visualization
    \item AST: Project administration, Supervision, Conceptualization,  Writing--major reviews and edits, Resources, Visualization, Sharing rules
    \item SM: Conceptualization, Writing--major reviews and edits, Resources, Visualization, Sharing rules
    \item YBS: Conceptualization, Writing--major reviews and edits, Resources
    \item HT: Conceptualization, Writing--major reviews and edits, Resources
    \item DHP: Conceptualization, Writing--major reviews and edits, Sharing rules
    \item MB: Conceptualization
    \item BA: Writing--major reviews and edits, Resources, Sharing rules
    \item LH: Writing--major reviews and edits, Resources, Sharing rules
    \item LA: Writing--major reviews and edits, Resources
    \item JPN: Writing--major reviews and edits, Visualization
    \item MAC: Writing--major reviews and edits
    \item FM: Writing--major reviews and edits
    \item RG: Writing--major reviews and edits
    \item NM: Sharing rules
    \item AU: Sharing rules
    \item JC: Sharing rules
    \item AE: Sharing rules
    \item SC: Sharing rules
    \item JR: Writing--major reviews and edits
\end{itemize}
